The thin blue line:\\what protects my Android device?

### 2015-04-02 securityupdates.tex
Manually make device data plots more efficient and put beneath each other on the same page to save space

{
\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{figures/device-data-all-security}
\caption{The top \daNumDeviceDataDevices\ devices by days of contribution in the \da\ data. One strip per device handset and each strip shows the number of vulnerabilities affecting each device over time.}
\label{fig:device_data_security}
\end{figure}
}

{
\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{figures/device-data-all-os}
\caption{The top \daNumDeviceDataDevices\ devices by days of contribution in the \da\ data. One strip per device handset and each strip shows OS versions over time. Black lines show where an update only changed the build number.}
\label{fig:device_data_os}
\end{figure}
}

%{\begin{figure}[p]
% \centering
% \begin{subfigure}[b]{\columnwidth}
%  \includegraphics[width=\columnwidth]{figures/device-data-all-os}
%  \caption{OS versions over time. Black lines show where only the build number changed.}
%  \label{fig:device_data_os}
% \end{subfigure}
% ~\\
% \begin{subfigure}[b]{\columnwidth}
%  \includegraphics[width=\columnwidth]{figures/device-data-all-security}
%  \caption{Number of vulnerabilities affecting each device over time}
%  \label{fig:device_data_security}
% \end{subfigure}
% \caption{The top \daNumDeviceDataDevices\ devices by days of contribution in the \da\ data. One strip per device handset.}
 % \includegraphics[width=\columnwidth]{figures/nw_security_updates.pdf}
 %\caption{Proportion of updates each week which (may have) fixed vulnerabilities}
 %\label{fig:weekly_security_updates}
%\end{figure}}

>>>>

{
\begin{figure}[!t]
\centering
\begin{subfigure}{\columnwidth}
\includegraphics[width=\columnwidth]{figures/device-data-all-security}
\vspace{-1.5em}
\caption{Each strip shows the number of vulnerabilities affecting each device over time.}
\label{fig:device_data_security}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=\columnwidth]{figures/device-data-all-os}
\vspace{-1.5em}
\caption{Each strip shows OS versions over time. Black lines show where an update only changed the build number.}
\label{fig:device_data_os}
\end{subfigure}
\caption{The top \daNumDeviceDataDevices\ devices by days of contribution in the \da\ data. One strip per device handset.}
\end{figure}
}
